---
title: "scheduler Tags"
author: "Eric Bailey"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Vignette Title}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

The scheduler package uses specially decorated comments similar to `roxygen2` 
and `plumber`. These comments allow a user to create scripts that will run at 
specified times. For scheduler these comments look like this `#*`. scheduler 
follows a convention similar to roxygen. The first scheduler comment will be 
interpreted as the scripts name. This name will be used to identify the script
in any logs. This is required in every scheduler script.

Next, like in roxygen2, there is an optional description block. This may be used
in future GUI development and is helpful to remind you what your scripts intended
purpose is. This block is currently optional.

Next can be a series of tags. Currently, there are only two scheduler tags `@when`
and `@log`. A functional scheduler script may look like this:

```{r, eval=FALSE}
#* Test Job
#*
#* This is an example of a scheduler script. It doesn't do much. but
#* it illustrates the basics of how a script should be layed out. It prints
#* Hello World with a start on either side.
#*
#* @when wednesday first last 10:00
#* @log info

library(clisymbols)
library(crayon)

cat(yellow(symbol$star), bold("Hello World!"), yellow(symbol$star))
```

## Vignette Info

Note the various macros within the `vignette` section of the metadata block above. These are required in order to instruct R how to build the vignette. Note that you should change the `title` field and the `\VignetteIndexEntry` to match the title of your vignette.

## Styles

The `html_vignette` template includes a basic CSS theme. To override this theme you can specify your own CSS in the document metadata as follows:

    output: 
      rmarkdown::html_vignette:
        css: mystyles.css

## Figures

The figure sizes have been customised so that you can easily put two images side-by-side. 

```{r, fig.show='hold'}
plot(1:10)
plot(10:1)
```

You can enable figure captions by `fig_caption: yes` in YAML:

    output:
      rmarkdown::html_vignette:
        fig_caption: yes

Then you can use the chunk option `fig.cap = "Your figure caption."` in **knitr**.

## More Examples

You can write math expressions, e.g. $Y = X\beta + \epsilon$, footnotes^[A footnote here.], and tables, e.g. using `knitr::kable()`.

```{r, echo=FALSE, results='asis'}
knitr::kable(head(mtcars, 10))
```

Also a quote using `>`:

> "He who gives up [code] safety for [code] speed deserves neither."
([via](https://twitter.com/hadleywickham/status/504368538874703872))
